% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
%-----------------------------------------------------------
%\usepackage{fullpage}
%\usepackage[icelandic]{babel}
%\usepackage[swedish]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{shading}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-3pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Mikael Dubik}  & +354 8484903\\
Einholt 7 &  mkdubik@gmail.com \\
Reykjavík, Iceland & https://github.com/mkdubik \\
\end{tabular*}
\\

\vspace{0.05in}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{Uppsala University}{Uppsala, Sweden}{M.Sc., Computer Science}{Aug. 2015 - Sep. 2017}

\item
	\ressubheading{University of Iceland}{Reykjavík, Iceland}{B.Sc., Computer Science}{Aug. 2010 - Feb. 2014}

\item
	\ressubheading{Kvennaskólinn í Reykjavík}{Reykjavík, Iceland}{Matriculation}{2006-2010}

\end{itemize}

\resheading{Work Experience}
\begin{itemize}
\item
	\ressubheading{Marorka}{Reykjavík, Iceland}{Data engineer}{Oct. 2017 - Mar. 2018}
	\begin{itemize}
		\resitem{Design and implementation of an ETL system (Apache Kafka)}
		\resitem{Implementation and use of AWS EC2 and other AWS services}
	\end{itemize}

\item
	\ressubheading{Dohop}{Reykjavík, Iceland}{Server engineer and mobile developer}{May 2013 - Aug. 2015}
	\begin{itemize}
		\resitem{Maintenance of back end services and servers.}
		\resitem{Website crawling and writing web spiders.}
		\resitem{Implementation and deployment of Dohop for Android. Team leader.}
	\end{itemize}

\item
	\ressubheading{University of Iceland}{Reykjavík, Iceland}{Research and development}{May 2012 - Aug. 2012}
	\begin{itemize}
		\resitem{Part of a group working on virtual environment for crisis management training to complement live exercise training.}
		\resitem{Implemented voice recognition to control non-player characters in the virtual environment}
	\end{itemize}
\end{itemize}

\newpage
\resheading{Projects}
\begin{itemize}
\item
	\ressubheading{Uppsala University}{Uppsala, Sweden}{Multiplex network analysis, MSc Thesis}{Jan. 2017 - Sep. 2017}
	\begin{itemize}
		\resitem{A comparative evaluation of state-of-the-art clustering algorithms for multiplex networks}
		\resitem{Community detection in networks spanning multiple layers}
	\end{itemize}
\end{itemize}

\begin{itemize}
\item
	\ressubheading{BEST Uppsala}{Uppsala, Sweden}{Non-profit student organization}{Sep. 2015 - Sep. 2017}
	\begin{itemize}
		\resitem{Organized and managed a local Engineering competition}
		\resitem{President of BEST Uppsala}
	\end{itemize}
\end{itemize}

\begin{itemize}
\item
	\ressubheading{University of Iceland}{Reykjavík, Iceland}{Augmented reality with Python and OpenCV, BSc Project}{Aug. 2013 - Feb. 2014}
	\begin{itemize}
		\resitem{Designed and implemented a single player video game where only form of input was through computer vision}
		\resitem{Trained a haar classifier to recognize special objects}
	\end{itemize}
\end{itemize}

\resheading{References}
\begin{itemize}
\item
	\ressubheading{Steindór Sigurðsson}{}{Director of Research and Development, Marorka}{}
	\begin{itemize}
		\resitem{steindor.sigurdsson@marorka.com, +3548552000}
	\end{itemize}
	
\item
	\ressubheading{Matteo Magnani}{}{Senior lecturer at Department of Information Technology, Uppsala University}{}
	\begin{itemize}
		\resitem{matteo.magnani@it.uu.se, +46184714021}
	\end{itemize}

\item
	\ressubheading{Kristján Bjarnason}{}{CTO, Dohop}{}
	\begin{itemize}
		\resitem{kgb@dohop.com, +3545614848}
	\end{itemize}

\item
	\ressubheading{Ebba Þóra Hvannberg}{}{Professor at Faculty of Engineering and Computer Science, University of Iceland}{}
	\begin{itemize}
		\resitem{ebba@hi.is, +3548979196}
	\end{itemize}
\end{itemize}

\end{document}
